% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      

The journey of undertaking this Ph.D. has been a labour of love for me and it is a journey that I would not have been able to complete without the friendship and support of peers and mentors.

First, I would like to thank my supervisor, Kalina Bontcheva, for her unending support, generosity, grace and invaluable advice throughout the entire process.
I would also like to acknowledge Mehmet Bakir, my second supervisor for his advice and willingness to sit with me and work through technical challenges.
Here, I would also like to thank Andreas Vlachos without whom my technical knowledge and understanding would not be what it has become.

I would also like to take a moment to acknowledge the teachers and figures of authority throughout my childhood and youth who have found creative ways to discourage me from academic pursuits.\\
In contrast, I would like to thank Dirk Hovy, Joel Tetreault, Wendy Hui Kyong Chun, Barbara Plank, and Leon Derczynski for their advice for each talking me out of dropping out of the programme and encouraging me to flourish.
I cannot overstate my thanks to the workshop attendees and organisers at the Lorentz workshop who created an environment that showed that even within the elitist hostility and contempt of marginalised bodies that is academia, there are breathing spaces and homes to be found.

% Add Michael and Tech Neo Choo

Similarly so, I would also like to take a moment to thank my collaborators and co-conspirators, Nanna Bonde Thylstrup, Smarika Lulz, Isabelle Augenstein, James Thorne, and Joachim Bingel, Maya Indira Ganesh, Su Lin Blodgett, Dan Bareket, Anjalie Field, Bertie Vidgen, Aline Villavicencio, Joris van Hoboken and Frencien Dechene whose friendship and endless willingness to share their knowledge and expertise is reflected in every word.

I also acknowledge the musicians Chaka Khan and De La Soul, whose musical masterpiece "All Good" I quote in the title.

Throughout the time I've been working towards writing this dissertation, I have been organising and hosting workshops on online abuse and diversifying ACL conferences and the Natural Language Processing field.
I want to thank each of my co-organisers for the innumerable ways in which they've helped make me a more well rounded researcher.
I would also like to take this moment to apologise and thank my friends Adina, Nanna, Kayla, Dalton, Paul, and Yanai who have all suffered through drafts and the tortured prose in earlier drafts.

Throughout the time I have been working towards this dissertation, I have enjoyed the company and discussions of some of the smartest, most compassionate and kind people one could hope to make friends of.
Although a complete list of everyone would fill up another $180$ pages, I want to in particular thank Lianna, Rasmus, Tal, Hector, Martin, Kasper, Søren, Noam, Asbjørn, Carl Johan, Nikita, Mareike, Hannah, Deb, Alex, Abeba, Alison, Haiyang, Fred, Ryan, Teresa, Libby, Amittai, George, Hardy, Valentina, Suchin, Amandalynne, Chiraag, Megan, Vinod, Jacque, Nikos, Swabha, Elearnor, and Pranava who have helped, discussed, laughed, and argued with me, always just at the right time.

I would like to thank my mother, Talat, and sisters, Rushna, Tehneyat and Aqleema, who have supported me, shaped my thinking, kept me grounded, and taught me how to fly. I also want to thank my niece Sofia and my nephews, Aiden, Miles, and Lukas, whose love warms my bones and are my reasons to work on this topic.
Finally, I would like to acknowledge my partner, Fern to whom no amount of thanks can do justice in the ways she has helped me through this.
\end{acknowledgements}
